%---------------------------------------------------------------------
% Professional CV Template - Siqi Guo
% Optimized and cleaned version - 2025
%---------------------------------------------------------------------

\documentclass[a4paper]{article}

% ================ PACKAGES ================ %
\usepackage{geometry}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames, dvipsnames]{color}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{amsmath}

% ================ PAGE SETUP ================ %
\geometry{left=1.27cm, top=1.27cm, right=1.27cm, bottom=1.27cm}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Additional margin adjustments
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ================ CUSTOM FORMATTING ================ %
% Section formatting
\titleformat{\section}
    {\vspace{-10pt} \scshape \raggedright \large}
    {}
    {0em}
    {}
    [\color{black} \titlerule \vspace{-6pt}]

% Bullet styles
\renewcommand{\labelitemii}{$\circ$}
\setlist[itemize, 2]{label=$\bullet$}

% ================ EDUCATION COMMANDS ================ %
\newcommand{\resumeEducationSubHeadingListStart}{\begin{description}}
\newcommand{\resumeEducationSubHeadingListEnd}{\end{description}}
\newcommand{\resumeEducationSubheading}[4]{%
  \vspace{-1pt}\item
    \begin{tabular*}{0.98\textwidth}{@{\hspace{-0.5em}}p{0.8\textwidth}@{\extracolsep{\fill}}r@{}}
        \textbf{#1} & {#2} \\
        {#3} & {#4} \\
    \end{tabular*}%
  \vspace{-5pt}%
}
\newcommand{\courseList}[1]{%
  \vspace{0pt}
  \begin{description}[leftmargin=-25pt, style=unboxed]
    Relevant Courses: #1
  \end{description}
  \vspace{-5pt}
}

% ================ EXPERIENCE COMMANDS ================ %
\newcommand{\resumeExperienceSubHeadingListStart}{\begin{itemize}[label={}, leftmargin=*]}
\newcommand{\resumeExperienceSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeExperienceSubheading}[6]{
  \vspace{5pt}\item
    \begin{tabular*}{0.98\textwidth}{@{\hspace{-0.5em}}l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} & {#2} \\
      {#3} & {#4} \\
      {#5} & {#6}
    \end{tabular*}
  \vspace{-6pt}
}

\newcommand{\resumeExperienceItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeExperienceItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeExperienceItem}[1]{\item{{#1 \vspace{-1pt}}}}

\newcommand{\resumeExperienceSubItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeExperienceSubItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeExperienceSubItem}[2]{
  \item{
    \textbf{#1}
    {#2 \vspace{-2pt}}
  }
}

% ================ PROJECTS COMMANDS ================ %
\newcommand{\resumeProjectsSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeProjectsSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeProjectsSubHeading}[2]{
  \vspace{-1pt}
  \item{
    \begin{tabular*}{0.98\textwidth}{@{\hspace{-0.5em}}l@{\extracolsep{\fill}}r}
      \textbf{#1} & {#2} \\
    \end{tabular*}
  \vspace{-8pt}
  }
}
\newcommand{\resumeProjectsItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeProjectsItemListEnd}{\end{itemize}\vspace{0pt}}
\newcommand{\resumeProjectsItem}[1]{\item{{#1} \vspace{-2pt}}}

% ================ SKILLS COMMANDS ================ %
\newcommand{\resumeSkillsSubHeadingListStart}{\begin{description}}
\newcommand{\resumeSkillsSubHeadingListEnd}{\end{description}}
\newcommand{\resumeSkillsSubItem}[2]{
  \item\hspace{-0.8em}{
    \textbf{#1}{: \small{#2} \vspace{-2pt}}
  }
  \vspace{-3pt}
}

% ================ DOCUMENT CONTENT ================ %
\begin{document}

%-----------------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\centerline{\LARGE Siqi Guo} \vspace{5pt}} \\
  \centerline{\faEnvelope ~: \href{mailto:siqiguo@andrew.cmu.edu}{siqiguo@andrew.cmu.edu} | \faIcon{linkedin} \href{https://www.linkedin.com/in/siqiguo047/?locale=en_US}{: linkedin.com/in/siqiguo047} | \faPhone ~: (+1) 412-612-0495 | \faGlobe \href{https://guo-lab.github.io}{: https://guo-lab.github.io}} \\
\end{tabular*}

%----------------EDUCATION-----------------
\section{Education}
\resumeEducationSubHeadingListStart
\resumeEducationSubheading
{Carnegie Mellon University} {Pittsburgh, PA}
{Master of Science in Electrical and Computer Engineering; \quad GPA: 3.89/4.0} {May 2025}
\newline{}
\courseList{Foundations of Computer Systems, Embedded System Software Engineering, Distributed Systems, Autonomous Control System, Storage Systems, Modern Computer Architecture and Design, Intro to Embedded Systems, Multi-Agent Planning and Coordination, Software Development for Computational Science}

\resumeEducationSubheading
{Tianjin University} {Tianjin, China}
{Bachelor of Science in Computer Science and Technology; \quad GPA: 3.84/4.0} {June 2023}
\newline{}
\courseList{Data Structure, Operating System, Computer Networks, Principles of Database, Parallel Computing, Natural Language Processing, Pattern Recognition and Deep Learning}

\resumeEducationSubHeadingListEnd

%---------- EXPERIENCE -----------
\section{Research \& Industry Experience}
\resumeExperienceSubHeadingListStart

\resumeExperienceSubheading
{Eigenbot - Bio-inspired Distributed Control for Modular Robot} {Pittsburgh, PA}
{Biorobotics Lab Research Assistant (Part-time)} {Dec 2023 - Oct 2024}
{Advisor: Professor Howie Choset, Research Scientist Lu Li} {Carnegie Mellon University}
\resumeExperienceSubItemListStart
\resumeExperienceSubItem{Eigenbot Firmware Development and Testing}{
  \resumeExperienceItemListStart
  \resumeExperienceItem{Developed Eigenbot EEPROM parameters auto-setting tools, which accelerated Hexapod gaits tuning process.}
  \resumeExperienceItem{Tested the firmware. Redesigned and debugged the module communication protocol to ensure the robot's stability and reliability. Conducted the experiments with Logan, analyzed the gaits and fine-tuned firmware parameters.}
  \resumeExperienceItem{Integrated Foot Sensor Feedback into the robot's message protocol.}
  \resumeExperienceItem{Collected EigenBot's data from the real-world using OptiTrack, developing a pipeline to assess metrics like Gait Phase Difference and Leg Stance Duration, benchmarking its performance with centralized predefined gait.}
  \resumeExperienceItemListEnd
}
\resumeExperienceSubItemListEnd

\resumeExperienceSubheading
{Cepton, Inc.} {San Jose, CA}
{Software Engineer Intern → Software Engineer (Full-time)} {May 2025 - Nov 2025}
{LiDAR Technology Company} {}
\resumeExperienceSubItemListStart
\resumeExperienceSubItem{MST (Magnosteer Control) System Development}{
  \resumeExperienceItemListStart
  \resumeExperienceItem{Developed embedded \textbf{PD control algorithms with feedforward} for precision mirror movement control in LiDAR systems, implementing encoder auto-calibration and trajectory interpolation in \textbf{C/C++}.}
  \resumeExperienceItem{Optimized embedded system architecture by redesigning \textbf{SPI transfers and event queues}, achieving \textbf{73\% CPU utilization reduction} (90\% → 24\%) on ARM-based controllers.}
  \resumeExperienceItem{Built comprehensive \textbf{control simulation framework} in C and Python for algorithm validation, enabling systematic benchmarking of PD vs. PD-with-feedforward control strategies.}
  \resumeExperienceItem{Engineered real-time \textbf{MST GUI and debug logging system} in \textbf{Rust}, providing field engineers with live system monitoring and parameter tuning capabilities.}
  \resumeExperienceItem{Delivered \textbf{72\% power consumption reduction} (2.9W → 0.8W) on Ultra B3.3 120° LiDAR units through embedded firmware optimization and Python-based power analysis tools.}
  \resumeExperienceItemListEnd
}
\resumeExperienceSubItemListEnd

\resumeExperienceSubHeadingListEnd

%---------------- PROJECTS -----------------
\section{Projects}

\resumeProjectsSubHeadingListStart
\resumeProjectsSubHeading{{CloudFS, a Deduplicated Cloud File System} {| \href{https://github.com/Guo-lab/CloudFS_Design}{CMU 18-746 Course Project \faIcon{github}}}}{Oct 2024 - Dec 2024}
\resumeProjectsItemListStart
\resumeProjectsItem{Implemented CloudFS, leveraging the properties of local SSD and cloud storage to make data-placement decisions.}
\resumeProjectsItem{Identified and eliminated duplicate data with Rabin fingerprinting. Minimized storage usage and optimized data transfer in the form of segments. Designed buffer file to manually handle the file data transfer.}
\resumeProjectsItem{Implemented the IOCTL functions to support snapshot operations, such as create, restore, install, and uninstall.}
\resumeProjectsItem{Added in-memory LRU caching to further improve performance and reduce cloud operation costs, reaching \textbf{NO.1} on the scoreboard among all students.}
\resumeProjectsItemListEnd

\resumeProjectsSubHeading{{Distributed File System Design} {| \href{https://github.com/Guo-lab/15640-Distributed-Systems}{CMU 15-640 Course Project \faIcon{github}}}}{Feb 2024 - Apr 2024}
\resumeProjectsItemListStart
\resumeProjectsItem{Implemented the serialization protocol for the low-level RPC stub, supporting several RPCs in project's NFS.}
\resumeProjectsItem{Designed a File-Caching Proxy based on RMI. Implement open-close session semantics for proxy operations, and the LRU replacement policy for cache management. Used version control, check-on-use and last-close-win to make sure the proxy's cache and server freshness.}
\resumeProjectsItem{Implemented and Tuned a 3-Tier Architecture Scalable Web Service to satisfy dynamic or unexpected workloads by auto-scaling. Then, evaluated the performance of the system by benchmarking and figuring out the bottleneck.}
\resumeProjectsItem{Designed a Two-phase Commit Protocol to ensure the consistency of the distributed file system. Customized a mechanism to recovering from nodes failures and handling lost messages.}
\resumeProjectsItemListEnd

\resumeProjectsSubHeadingListEnd

%---------------- SKILLS -----------------
\section{Skills}
\resumeSkillsSubHeadingListStart
\resumeSkillsSubItem{Programming Languages}{C/C++, Python, Rust, C\#, LaTeX, SQL, Verilog, Bash}
\resumeSkillsSubItem{Frameworks}{TensorFlow, PyTorch, ROS, NodeJS, .NET, React}
\resumeSkillsSubItem{Software and Tools}{GIT, Docker, MySQL, Visual Studio Code, Gem5, PSoC, Vitis}
\resumeSkillsSubItem{Platforms}{MacOS, Linux, Arduino, GCP}
\resumeSkillsSubHeadingListEnd

\end{document}